---
title: "R Markdown Example"
author: "İlayda Çelenk"
date: "30/09/2023"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Part 1

# Big Section Headers  
## Small Section Headers  
### Smaller Section Headers  
**Bold**  
_Italic_  
line break: use an empty line or two spaces after the sentence.

itemization:

+ trial 1  
+ trial 2


## R Markdown

You can add code chunks and write your R codes in them:

```{r}
x <- 3
x = 2
x
```


```{r}
x=c(1,2,3,4)
print(x)
```

eval=FALSE: do not run code chunk, but it is visible.

```{r,eval=FALSE}
a<-3
a
```

warning=FALSE: warning messages do not appear.

```{r,warning=FALSE}

```

echo=FALSE:  do run code chunk, but it is not visible.

```{r,echo=TRUE}

```

You can combine those parameters.

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

## Knit to HTML

You can provide this work in html or pdf by clicking on knit to HTML of PDF buttons on RStudio.
